COG-ED Manuscript

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
calculated d prime

  }
```

@@

@@

>>>>

  # remove temporary variables

  remove(tempone, temptwo, tempthree, tempfour)

@@

  # remove temporary variables

  remove(mean_hitrate, sd_hitrate, mean_falsealarmrate, sd_falsealarmrate)

@@

      # make a temporary copy of the dprime data frame without 1-back

      h1a_data <- dprime[dprime$level != 1,]
      h1a_data$level <- as.factor(h1a_data$level)

      # define contrasts

      contrasts(h1a_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))

      # calculate ANOVA

      hypothesis1a_anova <- summary(aov(h1a_data$d ~ h1a_data$level))
      hypothesis1a_posthoc <- TukeyHSD(aov(h1a_data$d ~ h1a_data$level))
      remove(h1a_data)
